Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
hard to distinguish methods on roc curves
inverse curve fig + concl

The area under the ROC curve is not consistent metric
with respect to the problem statement. We advice to avoid the AUROC
for the assessment of network inference method. An alternative metric would
be the area under the precision-recall curve (AUPRC). Those
conclusions are in line with \cite{schrynemackers2013protocols}.

@@

Obviously, we give a hint about limiting the depth of trees in the GENIE3
method to infer the network. It should be interesting to see if there is a
optimum value for the maxmimal depth.

>>>>

The area under the ROC curve is not consistent metric
with respect to the problem statement. A clear hierachy is also difficult to derive based on ROC curve of Figure \ref{fig:curves}. We advice to avoid the AUROC
for the assessment of network inference method. An alternative metric would
be the area under the precision-recall curve (AUPRC). Those
conclusions are in line with \cite{schrynemackers2013protocols}.

@@

In the discussion, we give hints about limiting the depth of trees in the GENIE3
method to infer the network. It should be interesting to see if there is a
optimum value for the maxmimal depth. And of course, it may also rewarding to increase considerably the number of trees to get more stable predictions.
